Analyzing the Impact of Social Attributes on Commit Integration Success

### 2017-03-28 Paper/MSRChallenge2017.tex
revisions to the threats to validity and other minor updates

The precision, recall and
F-measure are calculated over the successful and unsuccessful classes and then
averaged (standard procedure in Weka).  All these measures, along with the Kappa
statistic, increase with social features, which provide evidence that social 
factors improve build success predictions. The mean 
absolute error decreases in both cases, further substantiating the importance 
of social factors
in predicting build success.

@@

%\paragraph{Internal validity}
We have made our scripts, data, and decision tree results publicly 
available\footnote{https://goo.gl/CqTX44}. 
We released these files for
extension, reproducibility, and further investigation of results.
In the study, we use Weka, a well known machine-learning toolkit,
to analyze our data.
Like all tools, Weka may contain bugs. 
Nonetheless, it is a community tested open source tool, which mitigates threats to 
internal validity. 
We mitigate the risk that our results fail to 
%\paragraph{External validity} 
generalize externally by studying a broad and rich 
data set~\cite{msr17challenge} comprising 1,359 popular projects.
Similarly, the social factors we study may not apply to closed-source
applications; however, open-source ecosystems are intellectually
valuable sources of study on their own. 
%
 Other concerns include the possibility that social factors
 have changed significantly in the past three years, that unsuccessful
 builds are due to
 incorrect test cases (rather than low quality contributions), and that
 information is lost in collapsing commits' multiple builds. We believe these
 are similarly mitigated by a large and varied data set, but leave investigation
 of the effects of these decisions to future work.

@@

The most similar related work to this paper is a case study investigating how
social and technical factors affect build
success on a project with 40 developers~\cite{Hassan06}.
In contrast to this work, we focus on a wide range of open source projects and
measure experience through developer profile information.
Other work has investigated the effects of various factors, such as team
organization, on predicting build success in a single
project~\cite{Kwan11,Wolf09}.
Previous investigations have established relationships between both social and 
technical 
attributes and 
different measures of success, such as pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse} or evaluation latency~\cite{Yu15}.
Gousios et al.~\cite{gousios14} found that the commit change location is
an important indicator to commit acceptance rate, and that including
test cases increases a
commit's acceptance rate~\cite{gousios15}.
Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, while Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. By contrast with their work, we focus on the relationship between social 
attributes and continuous integration success.

@@

We have analyzed how technical and social factors can be used to
predict high quality open source contributions, as measured by continuous
integration build success.  We have found that these factors can
insight when predicting the success of a build; technical factors led
to a 14\% increase in predictive power, and adding social factors led to another
12\% increase.

Overall, we conclude that social attributes proxying experience, such as whether
the developer is a core project contributor,
noticeably influence build success prediction, especially on the downsampled
data. 
%These results suggest that social factors
%are significant predictors when
%evaluating the predictive power of build commit success.
%
In particular, core team members are
more likely to have the build integration pass than non-core team members.  This
result provides evidence that non-core team member commits may not be
scrutinized as closely as core team member commits before the integration build 
tests,
although further study is required to draw definitive
conclusions.
%
Likewise, developers with more followers are more
likely to pass the build.
Developers with 1000+ followers were more than 10\% more succesful in their
builds compared to
developers with no followers.  This suggests that open source developers with
high quality commits may be more
likely to have a large number of followers.
Although we find experience is an imperfect indicator, 
experienced developers appear more likely to make high quality commits.

>>>>

The precision, recall, and
F-measure are calculated over the successful and unsuccessful classes and then
averaged (standard in Weka).  All these measures, along with the Kappa
statistic, increase with social features, which provide evidence that social 
factors improve build success predictions. The mean 
absolute error also decreases, further substantiating the importance 
of social factors
in predicting build success.

@@

%\paragraph{Internal validity}
In the study, we use Weka, a well known machine-learning toolkit,
to analyze our data.
Like all tools, Weka may contain bugs. 
Nonetheless, it is a community tested open source tool, which mitigates threats to 
internal validity. We also release our scripts, data, and decision tree 
results in the study\footnote{https://goo.gl/CqTX44}.

We mitigate the risk that our results fail to 
%\paragraph{External validity} 
generalize externally by studying a broad and rich 
data set~\cite{msr17challenge} comprising 1,359 popular projects.
Similarly, the social factors we study may not apply to closed-source
applications; however, open-source ecosystems are intellectually
valuable sources of study on their own. 
%
 Other concerns include the possibility that social factors
 have changed significantly in the past three years, that unsuccessful
 builds are due to
 incorrect test cases (rather than low quality contributions), and that
 information is lost in collapsing commits' multiple builds. We believe these
 are similarly mitigated by a large and varied data set, but leave investigation
 of the effects of these decisions to future work.

@@

The most similar related work to this paper is a case study investigating how
social and technical factors affect build
success on a project with 40 developers~\cite{Hassan06}.
In contrast to this work, we focus on a wide range of open source projects and
measure experience through developer profile information.
Other work has investigated the effects of various factors, such as team
organization, on predicting build success in a single
project~\cite{Kwan11,Wolf09}.
Previous investigations have established relationships between both social and 
technical 
attributes and 
different measures of success, such as pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse} or evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} 
show the importance of the social connection between the developer initiating a
pull request and the project integrators. We look at a broader aspect of 
social factors, and focus on predicting the Travis CI build success.
Gousios et al.~\cite{gousios14} found that the commit change location is
an important indicator to commit acceptance rate, and that including
test cases increases a
commit's acceptance rate~\cite{gousios15}.
Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, while Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. By contrast with their work, we focus on the relationship between social 
attributes and continuous integration success.

@@

We have analyzed how technical and social factors can be used to
predict high quality open source contributions, measured by continuous
integration build success.  We found social factors improve predictions of build 
success; technical factors led to a 14\% increase in predictive power, and 
adding social factors led to another 12\% increase.

Overall, we conclude that social attributes proxying experience, such as whether
the developer is a core project contributor,
noticeably influence build success prediction, especially on the downsampled
data. 
%These results suggest that social factors
%are significant predictors when
%evaluating the predictive power of build commit success.
%
In particular, core team members are
more likely to have the build integration pass than non-core team members.  This
result provides evidence that non-core team member commits may not be
scrutinized as closely as core team member commits before the integration build 
tests,
although further study is required to draw definitive
conclusions.
%
Likewise, developers with more followers are more
likely to pass the build.
Developers with 1000+ followers were more than 10\% more succesful in their
builds compared to
developers with no followers.  This suggests that open source developers with
high quality commits may be more
likely to have a large number of followers.

Although we find experience is an imperfect indicator, 
experienced developers appear more likely to make high quality commits.
